\begin{minipage}[t]{\linewidth}\vspace{\sectionTopmargin}
{\titleFont\light I'VE WORKED AS\ldots}\newline

\vspace{\titleBottomMargin}
{\subtitleFont\bold SOFTWARE ENGINEER \extraLight\scshape @ Centili}\newline
\vfill\vspace{\dateTopMargin}{\dateFont\extraLight Aug 2019--present\alignRight}\linebreak\newline

{\vspace{\contentTopMargin}\contentFont \begin{itemize}
    \item --Developed a custom API Gateway system and accompanying YAML config format, utilizing it to streamline and serve all Centili's new public APIs.
    \item --Taken a significant part in developing a multi-tenant storefront app and adapting the infrastructure to make a successful launch on Google Kubernetes Engine, making it the company's first service to go live on the cloud.
    \item --Migrated parts of a live production system which processes 1.5 million payment transactions daily from RMI to HTTP, and then to cloud.
    \item --Containerized and upgraded CI/CD, supporting legacy JBoss apps, Spring Boot (Java 11 and Java 17), React and serverless projects (Cloudflare Pages).
    \item --Migrated the monitoring stack (Prometheus, Alertmanager, Grafana) to K8s.
    \item --Used Cloudflare Workers to cut loading time of payment pages for up to 2s.
    \item --Designed and developed a dozen greenfield Spring Boot microservices.
    \item --Fixed a few bugs and built a few pages using React for our admin dashboard.
\end{itemize}}
\end{minipage}\newline% I don't want any kind of space here
%
\begin{minipage}[t]{\linewidth}\vspace{\subsectionSpace}%
{\subtitleFont\bold TEACHING ASSOCIATE \extraLight\scshape @ University of Belgrade, Faculty of Mathematics}\newline
\vfill\vspace{\dateTopMargin}{\dateFont\extraLight Oct 2022--Oct 2023\alignRight}\linebreak\newline

{\vspace{\contentTopMargin}\contentFont \begin{itemize}
\item --Taught practical classes and exercises for Computer Networks and Database Programming courses in 2022/23 (total 98 students in my groups).
\item --Creating and administering practical exams for courses I taught.
\end{itemize}}%
\end{minipage}%