\begin{minipage}[t]{\linewidth}\vspace{\sectionTopmargin}
{\titleFont\light I'VE STUDIED AT\ldots}\newline

\vspace{\titleBottomMargin}


{\subtitleFont\bold UNIVERSITY OF BELGRADE \vspace{0.75mm}\newline\extraLight\scshape Faculty of Mathematics}\newline

{\vspace{-3mm}\dateFont\extraLight MSc Informatics, 60ECTS | Nov 2022--Present}\newline
\vspace{-3mm}
{\contentFont \begin{itemize}
    \item --Took courses in algorithms, machine learning, software verification, software development and cryptography.
    \item --Built a 5-microservice \cvLink{https://github.com/luka-j/matf-rs2-api-gateway/}{API Gateway system} in ASP.NET Core and set up cloud Kubernetes infrastructure (C\#, Terraform, team).
    \item --Trained \cvLink{https://github.com/luka-j/matf-ml-outlier-detection/}{machine learning models} for outlier detection (Python, pairwork).
    \item --\cvLink{https://github.com/luka-j/LINVAST}{Added support for Go language} to an open source tool which generates language-invariant AST based on source code (C\#, pairwork).
\end{itemize}}
\end{minipage}\newline%
%
\begin{minipage}[t]{\linewidth}\vspace{\subsectionSpace}
{\subtitleFont\bold UNIVERSITY OF BELGRADE \vspace{0.75mm}\newline\extraLight\scshape Faculty of Mathematics}\newline

{\vspace{-3mm}\dateFont\extraLight BSc Informatics, 240ECTS | Oct 2018--Jun 2022}\newline
\vspace{-3mm}
{\contentFont \begin{itemize}
    \item --Built an app which \cvLink{https://gitlab.com/matfpveb/projekti/2021-2022/08-Giten-Tag}{creates a dev profile} based on GitHub commit stats (Node.js, Angular, team).
    \item --Built a \cvLink{https://gitlab.com/matf-bg-ac-rs/course-rs/projects-2021-2022/13-Git-stat}{read-only Git GUI} with GitLab support (C++, Qt, team).
    \item --Created a \cvLink{https://github.com/luka-j/stat-proj/}{web dashboard} for high school enrolment stats (R, pairwork).
    \item --Programmed a \cvLink{https://github.com/pearpanda/computer-graphics-project/}{bouncing ball animation} (OpenGL, pairwork).
    \item --Developed a configurable \cvLink{https://github.com/luka-j/ballistic-projectile/}{flight path simulator} (Python, individual).
\end{itemize}}
\end{minipage}\newline%
%
\begin{minipage}[t]{\linewidth}\vspace{\subsectionSpace}
{\subtitleFont\bold MATHEMATICAL GRAMMAR SCHOOL}\newline
{\vfill\vspace{\dateTopMargin}\dateFont\extraLight Sep 2014--Jun 2018\alignRight}\linebreak\newline

\vspace{\contentTopMargin}
{\contentFont \begin{itemize}
    \item --Graduated from a \cvLink{https://en.wikipedia.org/wiki/Mathematical_Grammar_School}{high school} for gifted students of maths, physics and CS.
    \item --My \cvLink{https://www.mg.edu.rs/uploads/files/images/stories/dokumenta/maturski/luka-jovicic.pdf}{graduation thesis} on data scraping and analysis was selected as \cvLink{https://www.mg.edu.rs/sr/nastava/najbolji-maturski-radovi}{one of the best informatics theses} for school year 2017/18.
\end{itemize}}
\end{minipage}\newline%