\begin{minipage}[t]{\linewidth}
{\titleFont\light PERSONAL PROJECTS}\newline

\vspace{\titleBottomMargin}
{\subtitleFont\bold STORIES \extraLight\scshape| Library \& Android app \href{https://github.com/luka-j/stories}{\faGithub} \href{https://github.com/luka-j/StoriesApp}{\faGithub}}\newline

\vspace{\ribbonTopMargin}
\ribbonJava \ribbonAndroid \ribbonPlay \ribbonPostgres\newline
\vspace{\ribbonBottomMargin}

{\contentFont \begin{itemize}
    \item --Built a custom programming language for choose-your-adventure stories.
    \item --Developed an accompanying Android app and no-code editor.
    \item --Developed a marketplace for CYA stories.
    \item --Winner of Special prize for innovativity at Telekom Srbija Regional App Challenge 2018.
\end{itemize}}
\end{minipage}\newline%
%
\begin{minipage}[t]{\linewidth}\vspace{\subsectionSpace}
{\subtitleFont\bold UPIS SUITE \extraLight\scshape| Desktop \& Web apps \href{https://github.com/luka-j/UpisScraper}{\faGithub} \href{https://github.com/luka-j/UpisStats}{\faGithub} \href{https://github.com/luka-j/UpisDesktop}{\faGithub}}\newline

\vspace{\ribbonTopMargin}
\ribbonJava \ribbonPlay \ribbonSwing \ribbonPostgres \ribbonJavascript\newline
\vspace{\ribbonBottomMargin}

{\contentFont \begin{itemize}
    \item --Built a web scraper to collect high school enrolment data.
    \item --Implemented an enrolment simulator with support for custom rules.
    \item --Created a web app with SQL-like data plotting language.
    \item --Developed a desktop app with visual query builder and a performant plotter in Swing framework.
\end{itemize}}
\end{minipage}\newline%
%
\begin{minipage}[t]{\linewidth}\vspace{\subsectionSpace}
{\subtitleFont\bold CHAT SURVEYS \extraLight\scshape| Web apps \href{https://github.com/Runtime-T-error}{\faGithub}}\newline

\vspace{\ribbonTopMargin}
\ribbonR \ribbonTidyverse \ribbonPostgres \ribbonJava \ribbonSpringBoot\newline
\vspace{\ribbonBottomMargin}

{\contentFont \begin{itemize}
    \item --Hackathon project which aimed to transform surveys to conversations, with Facebook chatbot as a proof of concept. We placed \nth{3} at RAF Hakaton 2019.
    \item --My main role was interpreting existing engagement data and building interactive dashboard for future analytics using R's shiny framework.
    \item --I also supported the team when it came to infrastructure tasks.
\end{itemize}}
\end{minipage}\newline%
%
\begin{minipage}[t]{\linewidth}\vspace{\subsectionSpace}
{\subtitleFont\bold VIDEO COMPRESSOR \extraLight\scshape| Web app \href{https://github.com/luka-j/MediaCompressor}{\faGithub}}\newline

\vspace{\ribbonTopMargin}
\ribbonKotlin \ribbonSpringBoot \ribbonPostgres \ribbonFfmpeg\newline
\vspace{\ribbonBottomMargin}

{\contentFont\begin{itemize}
    \item --Created a web app which aimed to reduce video size without significant compromises in quality, mainly used by fellow students during 2020/2021.
    \item --It supports clustering, so job queue is distributed among multiple nodes.
\end{itemize}}
\end{minipage}\newline%
%
\begin{minipage}[t]{\linewidth}\vspace{\subsectionSpace}
{\subtitleFont\bold CV \extraLight\scshape| Interactive document \href{https://github.com/luka-j/CV/tree/latex-v3}{\faGithub}}\newline

\vspace{\ribbonTopMargin}
\ribbonLatex \ribbonFontAwesome \newline
\vspace{\ribbonBottomMargin}

{\contentFont\begin{itemize}
    \item --Everything you're looking at is a product of my \LaTeX proficiency \& patience.
    \item --It is designed from scratch and built on top of \texttt{minimal} document class.
    \item --Especially interesting was building clickable elements below, and making sure nothing falls apart on viewers which don't support such functionality.
\end{itemize}}
\end{minipage}\newline