\noindent
\rlap{\begin{ocg}{OCG 0}{HelpText}{0} %so basically I use OCG so these things pop up only when appropriate arrow is clicked; I also want all of these boxes to overlap, so I'm using rlap to make them use no space and overlap (but to have their content visible, on click of course). 
  {\parbox{\linewidth}{\contentFont Great, it works! You can use the \faChevronCircleRight \ next to a project name to see its description. Click the same arrow again to close. Or you can use this one: \hideocg{HelpText}{\faChevronCircleLeft}}}
\end{ocg}\newline}
\rlap{\begin{ocg}{OCG 1}{NotekeeperText}{0}
\noindent
  {\parbox{\linewidth}{\contentFont Productivity and collaboration app for groups of students attending the same school. Provides a streamlined way for collecting and sharing notes, questions and multimedia content for different courses. Includes course organizer and exam calendar. The app won \nth{2} prize at Sixth mt:s App competition (2016).\hideocg{NotekeeperText}{\faChevronCircleLeft}}}
\end{ocg}\newline}
\rlap{\begin{ocg}{OCG 2}{HttpClientText}{0}
\noindent
  {\parbox{\linewidth}{\contentFont Implementation of HTTP/1.1 protocol from the ground up, using plain TCP sockets in Java. Provides an option to manually configure connection pool and reuses sockets wherever appropriate. Exposes both blocking (with timeout) and non-blocking (callback-based) API. Provides common abstractions for sending and receiving textual, raw and file content. Transparently handles redirects, content and transfer encodings.\hideocg{HttpClientText}{\faChevronCircleLeft}}}
\end{ocg}\newline}
\rlap{\begin{ocg}{OCG 3}{LabInventoryText}{0}
\noindent
  {\parbox{\linewidth}{\contentFont Web app for managing laboratory inventory, used in a local hospital. Tailored specifically for their needs, it tremendously speeds up inventory tracking and reporting for medical and non-medical supplies. UI was specifically built to be intuitive to non-technical users and print-friendly. \hideocg{LabInventoryText}{\faChevronCircleLeft}}}
\end{ocg}\newline}
\rlap{\begin{ocg}{OCG 4}{BgBusText}{0}
\noindent
  {\parbox{\linewidth}{\contentFont Android app which simplifies navigation in Belgrade on foot and using public transport. It is built upon a few custom heuristic algorithms which take into account time of day, type of transport and how often it is deployed. After algorithms are run with different parameters, four best results are displayed to the user and drawn on the map. The app was awarded \nth{2} prize at Fifth mt:s App Competition (2015). \hideocg{BgBusText}{\faChevronCircleLeft}}}
\end{ocg}\newline}

\vspace{6mm}
\rule{\linewidth}{0.1mm}